Inference methods comparison for the simplified Naomi model

### 2023-03-27 src/naomi-simple_compare/comparison.Rmd
Success on merging KS results into mf_out_fine: now have dataframe of KS results at finest level with district, age, sex information available #24

```{r}
# To fix
# ks_helper("alpha_t1_out")
```

>>>>

```{r}
ks_rho_t1_out <- to_ks_df(par = "rho_t1_out", outputs = TRUE, id = mf_out_fine$id)

merge_to_mf_out_fine <- function(ks_df) {
  ks_df %>%
  select(-par) %>%
  left_join(
    mf_out_fine %>%
      rename("full_id" = "id") %>%
      tibble::rowid_to_column("index") %>%
      mutate(index = as.numeric(index))
  ) %>%
  select(-index)
}

ks_rho_t1_out <- merge_to_mf_out_fine(ks_rho_t1_out)

ks_alpha_t1_out <- to_ks_df(par = "alpha_t1_out", outputs = TRUE, id = mf_out_fine$id) %>%
  merge_to_mf_out_fine()

ks_lambda_t1_out <- to_ks_df(par = "lambda_t1_out", outputs = TRUE, id = mf_out_fine$id) %>%
  merge_to_mf_out_fine()
```
